\documentclass[11pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}

% Configuracion de hipervinculos (sin colores)
\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
    pdfauthor={Richard Pascual Huallpa Yapo},
    pdftitle={Richard Pascual Huallpa Yapo - Resume}
}

% Eliminar numeracion de paginas
\pagestyle{empty}

% Comando para encabezado centrado
\newcommand{\resumeheader}[3]{
    \begin{center}
        \textbf{#1} \\
        #2 \\
        #3
    \end{center}
}

% Comando para secciones
\newcommand{\resumesection}[1]{
    \vspace{0.5em}
    \noindent\textbf{#1}
    \vspace{0.2em}
    \hrule
    \vspace{0.3em}
}

% Comando para entradas de experiencia/educacion
\newcommand{\resumeentry}[4]{
    \textbf{#1} \hfill #2 \\
    #3 \hfill #4
}

% Comando para subseccion de experiencia con bullets
\newcommand{\resumesubentry}[1]{
    \begin{itemize}[leftmargin=*,topsep=0pt,itemsep=2pt]
        #1
    \end{itemize}
    \vspace{0.3em}
}

\begin{document}

% Encabezado
\resumeheader{Richard Pascual Huallpa Yapo}{
    ricpascual29@gmail.com $\bullet$ github.com/psskal $\bullet$ linkedin.com/in/richardpascualhuallpa \\
    Lima, Peru $\bullet$ Machine Learning \& Mechatronics Engineer
}{}

\vspace{1em}

% Educacion
\resumesection{Education}

\resumeentry{Universidad Peruana de Ciencias Aplicadas}{Lima, Peru}
{Mechatronics Engineering}{2021 -- Present}

\resumeentry{High-Performance Schools (COAR - Cusco)}{Cusco, Peru}
{Secondary Education}{2015 -- 2018}

% Experiencia
\resumesection{Experience}

\resumeentry{PSSKAL}{Lima, Peru}
{Software Engineer}{May 2025 -- Nov 2025}
\resumesubentry{
    \item Designed and launched a SaaS platform for restaurants with QR digital menus, POS, and real-time ordering (B2B).
    \item Modeled order states (placed, accepted, preparing, ready, served) and a prioritized kitchen view to shorten service times.
    \item Implemented granular roles and permissions (owner, manager, cashier, waiter, kitchen) with access control and auditability.
    \item Built metric dashboards (real-time sales, top dishes, activity) and per-restaurant branding to support Facebook/IG campaigns.
}

\resumeentry{Avrtec Peru}{Lima, Peru}
{Machine Learning Engineer}{Jan 2025 -- May 2025}
\resumesubentry{
    \item Worked with sensor streams and heavy-equipment logs to train predictive maintenance models and early-failure detection.
    \item Designed ingestion, cleaning, and labeling pipelines for operational data, aligning metrics with the field engineering team.
    \item Trained and validated models that improved safety and availability by reducing unplanned downtime.
    \item Automated model performance monitoring and actionable reports to optimize remote fleet utilization in mining.
}

% Leadership
\resumesection{Leadership \& Activities}

\resumeentry{Steel Royal Space}{Cusco, Peru}
{Co-founder}{Mar 2024 -- Oct 2024}
\resumesubentry{
    \item Led an experimental rocket project for the Latin American Space Challenge (Brazil), integrating aerodynamics, propulsion, avionics, and telemetry.
    \item Coordinated cross-disciplinary engineering teams and test campaigns to de-risk flight readiness.
    \item Defined system interfaces and integration checkpoints to align mechanical, electrical, and software workstreams.
}

% Skills
\resumesection{Hard Skills}

\textbf{Data Science \& ML:} Python (pandas, scikit-learn), predictive maintenance, anomaly detection, feature engineering \\
\textbf{MLOps \& Pipelines:} Data ingestion/cleaning/labeling, model validation, performance monitoring, reporting \\
\textbf{Analytics \& Simulation:} MATLAB, statistical analysis, dashboards (product metrics, operations) \\
\textbf{Software \& Systems:} Python, TypeScript, SQL/MySQL, MongoDB; C/C++ for embedded interfaces \\
\textbf{Collaboration:} Git, GitHub

% Idiomas
\resumesection{Languages}

Quechua: Native \hfill Spanish: Native \hfill English: A2 Level

% Soft skills
\resumesection{Soft Skills}

\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=2pt]
    \item Problem-solving and teamwork
    \item Analytical thinking and proactive learning
    \item Leadership, adaptability, and field collaboration
\end{itemize}

% Certifications
\resumesection{Certifications}

\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=2pt]
    \item Google Data Analytics | Google | 2025
    \item Embedded Software Development with C | Educba | 2024
    \item Embedded Software and Hardware Architecture | University of Colorado Boulder | 2024
    \item Rust Fundamentals | Duke University | 2024
    \item Sampling People, Networks and Records | University of Michigan | 2022
    \item Combining and Analyzing Complex Data | University of Maryland, College Park | 2022
    \item Questionnaire Design for Social Surveys | University of Michigan | 2023
    \item Framework for Data Collection and Analysis | University of Maryland, College Park | 2022
\end{itemize}

\end{document}
